The SMT Competition 2015--2018

### 2018-11-25 2018/report/table-winners-main.tex
Weights, disagreements, minor
Minor

\begin{table}[]
\begin{center}
\scalebox{.89}{\begin{tabular}{rcccc}

@@

Logic  & 2015                          & 2016                                & 2017                          & 2018                                  \\

@@

\multicolumn{1}{l}{}            & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                  \\ \cline{5-5} 

@@

\multicolumn{1}{r|}{ALIA}       & \multicolumn{4}{c|}{{[}Z3{]}}                                                                                                               \\ \cline{2-5} 

@@

\multicolumn{1}{r|}{AUFLIA}     & \multicolumn{4}{c|}{CVC4}                                                                                                                   \\ \cline{2-5} 
\multicolumn{1}{r|}{AUFLIRA}    & \multicolumn{4}{c|}{{[}Z3{]}}                                                                                                               \\ \cline{2-5} 
\multicolumn{1}{r|}{AUFNIRA}    & \multicolumn{1}{c|}{CVC4}     & \multicolumn{2}{c|}{vampire}                                        & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5} 
\multicolumn{1}{r|}{BV}         & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{Q3B}            & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5} 

@@

\multicolumn{1}{r|}{LIA}        & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{2}{c|}{{[}Z3{]}}                                         \\ \cline{2-5} 
\multicolumn{1}{r|}{LRA}        & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{2}{c|}{{[}Z3{]}}                                         \\ \cline{2-5} 
\multicolumn{1}{r|}{NIA}        & \multicolumn{4}{c|}{{[}Z3{]}}                                                                                                               \\ \cline{2-5} 
\multicolumn{1}{r|}{NRA}        & \multicolumn{1}{c|}{CVC4}     & \multicolumn{1}{c|}{Vampire}        & \multicolumn{1}{c|}{Redlog}   & \multicolumn{1}{l}{{[}Z3{]}/Vampire}  \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_ABV}    & \multicolumn{4}{c|}{Boolector}                                                                                                              \\ \cline{2-5} 

@@

\multicolumn{1}{r|}{QF\_ALIA}   & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_ANIA}   & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{1}{c|}{{[}Z3{]}}         \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_AUFBV}  & \multicolumn{3}{c|}{{[}MathSAT{]}}                                                                  & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_AUFLIA} & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_AUFNIA} & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{2}{c|}{{[}Z3{]}}                                         \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_AX}     & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_BV}     & \multicolumn{2}{c|}{Boolector}                                      & \multicolumn{2}{c|}{Boolector/MinkeyRink}                             \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_BVFP}   & \multicolumn{1}{c|}{Z3 (FP)}  & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5} 
QF\_DT                          & \multicolumn{1}{l}{}          & \multicolumn{1}{l|}{}               & \multicolumn{2}{c|}{CVC4}                                             \\ \cline{4-5} 
\end{center}
\caption{\label{tab:winners-main-1} Winners of the main track (part 1).}

\begin{table}[]
\begin{center}
\scalebox{.89}{\begin{tabular}{rcccc}
Logic  & 2015                          & 2016                                & 2017                          & 2018                                  \\
\multicolumn{1}{l}{}            & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                  \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_FP}     & \multicolumn{1}{c|}{Z3 (FP)}  & \multicolumn{1}{c|}{{[}MathSat5{]}} & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{COLIBRI}          \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_IDL}    & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{2}{c|}{Yices2}                                           \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_LIA}    & \multicolumn{3}{c|}{{[}MathSat{]}}                                                                  & \multicolumn{1}{c|}{SPASS-SATT}       \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_LIRA}   & \multicolumn{2}{c|}{Yices2}                                         & \multicolumn{2}{c|}{{[}Z3{]}}                                         \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_LRA}    & \multicolumn{4}{c|}{CVC4}                                                                                                                   \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_NIA}    & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{2}{c|}{CVC4}                                             \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_NIRA}   & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{2}{c|}{SMTRAT}                                           \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_NRA}    & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{1}{c|}{Yices2}   & \multicolumn{1}{c|}{{[}Z3{]}}         \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_RDL}    & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5} 

@@

\multicolumn{1}{r|}{QF\_UF}     & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_UFBV}   & \multicolumn{4}{c|}{Boolector}                                                                                                              \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_UFIDL}  & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_UFLIA}  & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{2}{c|}{Yices2}                                           \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_UFLRA}  & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_UFNIA}  & \multicolumn{1}{c|}{CVC4}     & \multicolumn{1}{c|}{Yices2/CVC4}    & \multicolumn{2}{c|}{Yices2}                                           \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_UFNRA}  & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{Yices2}         & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{Yices2}           \\ \cline{2-5} 
\multicolumn{1}{r|}{UF}         & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{1}{c|}{Vampire}  & \multicolumn{1}{c|}{CVC4/Vampire}     \\ \cline{2-5} 
\multicolumn{1}{r|}{UFBV}       & \multicolumn{4}{c|}{{[}Z3{]}}                                                                                                               \\ \cline{2-5} 

@@

\multicolumn{1}{r|}{UFIDL}      & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{1}{c|}{{[}Z3{]}}         \\ \cline{2-5} 
\multicolumn{1}{r|}{UFLIA}      & \multicolumn{4}{c|}{CVC4}                                                                                                                   \\ \cline{2-5} 
\multicolumn{1}{r|}{UFLRA}      & \multicolumn{1}{c|}{CVC3}     & \multicolumn{3}{c|}{{[}Z3{]}}                                                                               \\ \cline{2-5} 
\multicolumn{1}{r|}{UFNIA}      & \multicolumn{1}{c|}{CVC4}     & \multicolumn{2}{c|}{Vampire}                                        & \multicolumn{1}{c|}{{[}Z3{]}/Vampire} \\ \cline{2-5} 

@@

\end{center}
\caption{\label{tab:winners-main-2} Winners of the main track (part 2).}

>>>>

\begin{table}
\caption{Best main-track solvers (by division)}
\label{tab:winners-main}
\centering
\scalebox{.84}{\begin{tabular}{|rcccc|}

@@

Division                         & 2015                          & 2016                                & 2017                          & 2018                                  \\

@@

%\multicolumn{1}{l}{}            & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                  \\ \cline{5-5}

@@

\multicolumn{1}{|r|}{ALIA}       & \multicolumn{4}{c|}{{[}Z3{]}}                                                                                                               \\ \cline{2-5}

@@

\multicolumn{1}{|r|}{AUFLIA}     & \multicolumn{4}{c|}{CVC4}                                                                                                                   \\ \cline{2-5}
\multicolumn{1}{|r|}{AUFLIRA}    & \multicolumn{4}{c|}{{[}Z3{]}}                                                                                                               \\ \cline{2-5}
\multicolumn{1}{|r|}{AUFNIRA}    & \multicolumn{1}{c|}{CVC4}     & \multicolumn{2}{c|}{Vampire}                                        & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
\multicolumn{1}{|r|}{BV}         & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{Q3B}            & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}

@@

\multicolumn{1}{|r|}{LIA}        & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{2}{c|}{{[}Z3{]}}                                         \\ \cline{2-5}
\multicolumn{1}{|r|}{LRA}        & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{2}{c|}{{[}Z3{]}}                                         \\ \cline{2-5}
\multicolumn{1}{|r|}{NIA}        & \multicolumn{4}{c|}{{[}Z3{]}}                                                                                                               \\ \cline{2-5}
\multicolumn{1}{|r|}{NRA}        & \multicolumn{1}{c|}{CVC4}     & \multicolumn{1}{c|}{Vampire}        & \multicolumn{1}{c|}{Redlog}   & \multicolumn{1}{c|}{{[}Z3{]}/Vampire} \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_ABV}    & \multicolumn{4}{c|}{Boolector}                                                                                                              \\ \cline{2-5}

@@

\multicolumn{1}{|r|}{QF\_ALIA}   & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_ANIA}   & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{1}{c|}{{[}Z3{]}}         \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_AUFBV}  & \multicolumn{3}{c|}{{[}MathSAT{]}}                                                                  & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_AUFLIA} & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_AUFNIA} & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{2}{c|}{{[}Z3{]}}                                         \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_AX}     & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_BV}     & \multicolumn{2}{c|}{Boolector}                                      & \multicolumn{2}{c|}{Boolector/MinkeyRink}                             \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_BVFP}   & \multicolumn{1}{c|}{Z3}       & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
QF\_DT                           & \multicolumn{1}{l}{}          & \multicolumn{1}{l|}{}               & \multicolumn{2}{c|}{CVC4}                                             \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_FP}     & \multicolumn{1}{c|}{Z3}       & \multicolumn{1}{c|}{{[}MathSAT{]}}  & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{COLIBRI}          \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_IDL}    & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{2}{c|}{Yices2}                                           \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_LIA}    & \multicolumn{3}{c|}{{[}MathSAT{]}}                                                                  & \multicolumn{1}{c|}{SPASS-SATT}       \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_LIRA}   & \multicolumn{2}{c|}{Yices2}                                         & \multicolumn{2}{c|}{{[}Z3{]}}                                         \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_LRA}    & \multicolumn{4}{c|}{CVC4}                                                                                                                   \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_NIA}    & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{2}{c|}{CVC4}                                             \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_NIRA}   & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{2}{c|}{SMT-RAT}                                          \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_NRA}    & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{1}{c|}{Yices2}   & \multicolumn{1}{c|}{{[}Z3{]}}         \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_RDL}    & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5}

@@

\multicolumn{1}{|r|}{QF\_UF}     & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_UFBV}   & \multicolumn{4}{c|}{Boolector}                                                                                                              \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_UFIDL}  & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_UFLIA}  & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{2}{c|}{Yices2}                                           \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_UFLRA}  & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_UFNIA}  & \multicolumn{1}{c|}{CVC4}     & \multicolumn{1}{c|}{Yices2/CVC4}    & \multicolumn{2}{c|}{Yices2}                                           \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_UFNRA}  & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{Yices2}         & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{Yices2}           \\ \cline{2-5}
\multicolumn{1}{|r|}{UF}         & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{1}{c|}{Vampire}  & \multicolumn{1}{c|}{CVC4/Vampire}     \\ \cline{2-5}
\multicolumn{1}{|r|}{UFBV}       & \multicolumn{4}{c|}{{[}Z3{]}}                                                                                                               \\ \cline{2-5}

@@

\multicolumn{1}{|r|}{UFIDL}      & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{1}{c|}{{[}Z3{]}}         \\ \cline{2-5}
\multicolumn{1}{|r|}{UFLIA}      & \multicolumn{4}{c|}{CVC4}                                                                                                                   \\ \cline{2-5}
\multicolumn{1}{|r|}{UFLRA}      & \multicolumn{1}{c|}{CVC3}     & \multicolumn{3}{c|}{{[}Z3{]}}                                                                               \\ \cline{2-5}
\multicolumn{1}{|r|}{UFNIA}      & \multicolumn{1}{c|}{CVC4}     & \multicolumn{2}{c|}{Vampire}                                        & \multicolumn{1}{c|}{{[}Z3{]}/Vampire} \\ \hline

@@
